---
title: "Clean and filter water temps"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` 

Load libraries
```{r include=FALSE, results='hide'}

packs <- c('tidyverse', 'dataRetrieval', 'reshape2', 'scales', 'stringr',
           'leaflet', 'knitr', 'lubridate')
lapply(packs, require, character.only = T)
```

Load WQ and site info data into Environment
```{r echo=T, results='hide'}
CRB_Laketemp <- readRDS("D:/Sepulveda_USGS/BOR_mussel_waterquality/DreissenidWaterQuality/Data/raw/CRB_Laketemp_041219.rds")

CRB_Laketemp_siteinfo<- readRDS("D:/Sepulveda_USGS/BOR_mussel_waterquality/DreissenidWaterQuality/Data/raw/CRB_Laketemp_041219_siteInfo.rds")
```

Reduce file size
```{r}
CRB_Laketemp_reduced = CRB_Laketemp %>% 
  select(OrganizationFormalName,
         ActivityStartDate, ActivityStartTime.Time, ActivityStartTime.TimeZoneCode,
         ActivityDepthHeightMeasure.MeasureValue, ActivityDepthHeightMeasure.MeasureUnitCode,
         ActivityTopDepthHeightMeasure.MeasureValue, ActivityTopDepthHeightMeasure.MeasureUnitCode,
         ActivityBottomDepthHeightMeasure.MeasureValue, ActivityBottomDepthHeightMeasure.MeasureUnitCode,
         CharacteristicName,
         MonitoringLocationIdentifier,
         SampleCollectionMethod.MethodName, SampleCollectionEquipmentName,
         ResultMeasureValue, ResultMeasure.MeasureUnitCode, ResultSampleFractionText,
         ResultAnalyticalMethod.MethodName, MethodDescriptionText,
         ProviderName) %>% 
  filter(!is.na(ResultMeasureValue)) %>%  # get rid of NA values
  mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")   #get rid of white spaces
          )

ggplot(CRB_Laketemp_reduced, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```


Look at units for Water temps and the # of counts for each unit. 
```{r}
table(CRB_Laketemp_reduced$ResultMeasure.MeasureUnitCode) #
```

Convert deg F to deg C

```{r}
library(weathermetrics)

CRB_Laketemp_reduced = CRB_Laketemp_reduced %>% 
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "deg F" ~ (fahrenheit.to.celsius(ResultMeasureValue)),
                              TRUE~as.numeric(ResultMeasureValue))) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "deg F", "deg C",
                    ResultMeasure.MeasureUnitCode)) %>% 
  filter(ResultMeasure.MeasureUnitCode == "deg C") # limit to deg C since there are so few counts for other units.  


ggplot(CRB_Laketemp_reduced, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()

```

Alright, looks like a handful of temp values that don't make sense. I checked to make sure conversion of F to C worked... it did. Since these are likely F values recording with the wrong units or just crap. Regardless, we have to junk them since we have no confidence.  Maybe a logical place to start is to filter values < 35 C, since ~ 30 C is near their incipient upper thermal limit
```{r}
CRB_Laketemp_reduced = CRB_Laketemp_reduced %>% 
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "deg F" ~ (fahrenheit.to.celsius(ResultMeasureValue)),
                              TRUE~as.numeric(ResultMeasureValue))) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "deg F", "deg C",
                    ResultMeasure.MeasureUnitCode)) %>% 
  filter(ResultMeasure.MeasureUnitCode == "deg C") %>%  
  filter(!ResultMeasureValue > 34) %>%  #Get rid of these
  mutate(Month = lubridate::month(ActivityStartDate, label=TRUE))

ggplot(CRB_Laketemp_reduced, aes(x = Month, y = ResultMeasureValue))+
  geom_boxplot()
```


Simple look at # data points per month
```{r}
table(CRB_Laketemp_reduced$Month)
```


```{r}
CRB_Laketemp_reduced = CRB_Laketemp_reduced %>% 
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "deg F" ~ (fahrenheit.to.celsius(ResultMeasureValue)),
                              TRUE~as.numeric(ResultMeasureValue))) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "deg F", "deg C",
                    ResultMeasure.MeasureUnitCode)) %>% 
  filter(ResultMeasure.MeasureUnitCode == "deg C") %>%  
  filter(!ResultMeasureValue > 34)  %>%  #Get rid of these
  mutate(Month = lubridate::month(ActivityStartDate, label=TRUE)) %>% 
group_by(MonitoringLocationIdentifier) %>%
      summarise(count=n(),
                Waterstart=min(ActivityStartDate),
                Waterend=max(ActivityStartDate),
                Watermax = max(ResultMeasureValue, na.rm = TRUE),
                Watermean = mean(ResultMeasureValue, na.rm = TRUE),
                Waterstdev = sd(ResultMeasureValue, na.rm = TRUE)) %>% 
    left_join(CRB_Laketemp_siteinfo, by = "MonitoringLocationIdentifier") # join location information

#save Lake data file
saveRDS(CRB_Laketemp_reduced, "D:/Sepulveda_USGS/BOR_mussel_waterquality/DreissenidWaterQuality/Data/processed/CRB_Laketemp_reduced.rds")
```

Next enter parameters for mapping on leaflet.
You can change pH breakpoints in the risk.bins line.  
```{r}
pal = colorNumeric(
  palette = "Reds",
  domain = CRB_Laketemp_reduced$max)

```

Finally, plot it spatially via leaflet
```{r}
library(mapview)

leaflet(data=CRB_Laketemp_reduced) %>% 
      #addTiles() %>% for simple openstreet basemap
      addProviderTiles(providers$Esri.NatGeoWorldMap) %>%  
      addCircleMarkers(~dec_lon_va, ~dec_lat_va,
                       fillColor = ~pal(max),
                       radius = 2,  # to make size a function of count replace with ~sizes
                       fillOpacity = 0.8, opacity = 0.8,stroke=FALSE,
                       popup=~station_nm) %>%
      addLegend(position = 'bottomleft',
                pal=pal,
                values=~max,
                opacity = 0.8,
                labFormat = labelFormat(digits = 1), 
                title = 'Max Water Temp C') %>% 
  addMouseCoordinates(style = "basic") %>% 
  setView(lng = -118.3,
          lat = 45.6,
          zoom = 5)



```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
