---
title: "Explore & Filter CRB water data"
output: html_notebook
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
``` 

Load libraries
```{r include=FALSE, results='hide'}

packs <- c('tidyverse', 'dataRetrieval', 'reshape2', 'scales', 'stringr',
           'leaflet', 'knitr', 'lubridate')
lapply(packs, require, character.only = T)
```

Load WQ and site info data into Environment
```{r echo=T, results='hide'}
CRB_qw_040519 <- readRDS("D:/Sepulveda_USGS/BOR_mussel_waterquality/DreissenidWaterQuality/Data/raw/CRB_qw_040519.rds")

CRB_qw_siteinfo_040519 <- readRDS("D:/Sepulveda_USGS/BOR_mussel_waterquality/DreissenidWaterQuality/Data/raw/CRB_qw_siteinfo_040519.rds")
```




2. Simple cleanup of the data
```{r echo=T, results='hide'}
#To load already saved data, find file in directory and click on it
CRB_qw = CRB_qw_040519 %>% 
  filter(ActivityMediaName == "Water") %>% 
    filter(!is.na(ResultMeasureValue)) %>%  # get rid of NA values
    mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")   #get rid of white spaces
          ) %>%  
    filter(ActivityMediaName == "Water") %>% 
    filter(!is.na(ResultMeasureValue)) %>%  # get rid of NA values
    mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")   #get rid of white spaces
          ) %>% 
  select(OrganizationFormalName,
         ActivityStartDate, ActivityStartTime.Time, ActivityStartTime.TimeZoneCode,
         ActivityDepthHeightMeasure.MeasureValue, ActivityDepthHeightMeasure.MeasureUnitCode,
         CharacteristicName,
         MonitoringLocationIdentifier,
         SampleCollectionMethod.MethodName, SampleCollectionEquipmentName,
         ResultMeasureValue, ResultMeasure.MeasureUnitCode, ResultSampleFractionText,
         ResultAnalyticalMethod.MethodName, MethodDescriptionText,
         ProviderName)

siteInfo=CRB_qw_siteinfo_040519

```


Split dataset by 'charactersticName' and just cleanup and explore pH
```{r}
CRB_pH = as_tibble(CRB_qw)%>% 
   filter(CharacteristicName == "pH")

ggplot(CRB_pH, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```
  
  
That's awful. Let's first limit pH values to 0 -14
```{r}
CRB_pH = as_tibble(CRB_qw)%>% 
    filter(CharacteristicName == "pH") %>% 
    filter(!(ResultMeasureValue > 14|ResultMeasureValue <0))

ggplot(CRB_pH, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()

```


Better. Let's assume that these values are correct, but the units are wrong
```{r}
CRB_pH = as_tibble(CRB_qw)%>% 
    filter(CharacteristicName == "pH") %>% 
    filter(!(ResultMeasureValue > 14|ResultMeasureValue <0)) %>%
    mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =   
          ifelse(ResultMeasure.MeasureUnitCode %in% 
                   c("deg C", "NTU", "nu", "%", "mg/l",
                   "Mole/l", "std units", "ug/l",
                   "units/cm"), "None",
                 ResultMeasure.MeasureUnitCode))
  

ggplot(CRB_pH, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```


  Okay, let's call that good for now and start exploring the data. Here is the pH script that consolidates all of the previous scripts and adds a month column for each observation. 
```{r, eval=FALSE}
CRB_pH = CRB_qw %>% 
    filter(CharacteristicName == "pH") %>%
    filter(!(ResultMeasureValue > 14|ResultMeasureValue <0)) %>% 
    mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =   
             ifelse(ResultMeasure.MeasureUnitCode %in%
                     c("deg C", "NTU", "nu", "%", "mg/l",
                           "Mole/l", "std units", "ug/l", "units/cm"), "None",
                    ResultMeasure.MeasureUnitCode)) %>%
    mutate(Month = lubridate::month(ActivityStartDate, label=TRUE)) 
```

   
When are pH samples collected? Most are in summer... do we want to restrict pH to non-winter (i.e., mussel growing season)?
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(CRB_pH, aes(x = Month))+
  geom_histogram(stat="count")

```

Thinking more about how to filter pH data... does month of sampling matter? 
Mean stdev per month doesn't change much for the sites where 12 months data are available.  
```{r warning=FALSE}
CRB_pH_months= CRB_qw %>% 
  filter(CharacteristicName == "pH") %>%
  filter(!(ResultMeasureValue > 14|ResultMeasureValue <0)) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =   
           ifelse(ResultMeasure.MeasureUnitCode %in%
                    c("deg C", "NTU", "nu", "%", "mg/l",
                      "Mole/l", "std units", "ug/l", "units/cm"), "None",
                  ResultMeasure.MeasureUnitCode)) %>%
  mutate(Month = month(ActivityStartDate, label=TRUE)) %>% 
  group_by(MonitoringLocationIdentifier) %>%
  mutate(count = n_distinct(Month)) %>% #count how many unique months with pH data at a site
  filter(count == 12) %>% #limit data to just sites where data was collected every month
  group_by(MonitoringLocationIdentifier, Month) %>%  #summarize data at each site for each month
  summarise(max = max(ResultMeasureValue, na.rm = TRUE),
            mean = mean(ResultMeasureValue, na.rm = TRUE),
            stdev = sd(ResultMeasureValue, na.rm = TRUE))
  

ggplot(CRB_pH_months, aes(x = Month, y = stdev))+
  geom_boxplot()


```

But moving forward, let's code June, July, August and September samples as "High Quality" and all others as "Low Quality" 
```{r}
CRB_pH_monthsquality= CRB_qw %>% 
  filter(CharacteristicName == "pH") %>%
  filter(!(ResultMeasureValue > 14|ResultMeasureValue <0)) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =   
           ifelse(ResultMeasure.MeasureUnitCode %in%
                    c("deg C", "NTU", "nu", "%", "mg/l",
                      "Mole/l", "std units", "ug/l", "units/cm"), "None",
                  ResultMeasure.MeasureUnitCode)) %>%
  mutate(Month = month(ActivityStartDate, label=TRUE)) %>% 
  mutate(MonthQuality = ifelse(Month %in% c("Jun", "Jul", "Aug", "Sep"), "HighQuality", "LowQuality"))
```




How many samples have been collected at each site? Let's group the data by site and calculate some summaries 
```{r, eval=FALSE}
CRB_pH_summ = CRB_pH_monthsquality%>%
  filter(MonthQuality == "HighQuality") %>% 
group_by(MonitoringLocationIdentifier) %>%
      summarise(count=n(),
                start=min(ActivityStartDate),
                end=max(ActivityStartDate),
                max = max(ResultMeasureValue, na.rm = TRUE),
                mean = mean(ResultMeasureValue, na.rm = TRUE),
                stdev = sd(ResultMeasureValue, na.rm = TRUE))
```

    
Dot plot to view the # of data points at a site relative to pH stdeviation. Do we want to get rid of sites with a stdev > 1? 
```{r warning=FALSE}
ggplot(CRB_pH_summ, aes(x = count, y = stdev))+
  geom_point()+
  scale_y_continuous(limits = c(0,5))

```
   
   
Wow, some sites have been visited more than 1000 times.  What are these sites? Seems to be a mix of long-term monitoring and continuous sondes. 
```{r}
CRB_pH_summ %>% 
  arrange(desc(count)) %>% 
  head(n = 20)  # look at the top 20 sites

```
  
   
Look at data spatially using leaflet.
First, join spatial infor from siteInfo
```{r warning=FALSE}
CRB_pH = CRB_qw %>% 
    filter(CharacteristicName == "pH") %>%
    filter(!(ResultMeasureValue > 14|ResultMeasureValue <0)) %>% 
    mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =   
             ifelse(ResultMeasure.MeasureUnitCode %in%
                     c("deg C", "NTU", "nu", "%", "mg/l",
                           "Mole/l", "std units", "ug/l", "units/cm"), "None",
                    ResultMeasure.MeasureUnitCode)) %>%
    mutate(Month = month(ActivityStartDate, label=TRUE)) %>% 
    mutate(MonthQuality = ifelse(Month %in% c("Jun", "Jul", "Aug", "Sep"), "HighQuality", "LowQuality")) %>% 
    filter(MonthQuality == "HighQuality") %>%
  group_by(MonitoringLocationIdentifier) %>%
      summarise(count=n(),
                start=min(ActivityStartDate),
                end=max(ActivityStartDate),
                max = max(ResultMeasureValue, na.rm = TRUE),
                mean = mean(ResultMeasureValue, na.rm = TRUE),
                stdev = sd(ResultMeasureValue, na.rm = TRUE)) %>% 
    left_join(siteInfo, by = "MonitoringLocationIdentifier") # join location information

```


Next enter parameters for mapping on leaflet.
You can change pH breakpoints in the risk.bins line.  
```{r}

col_types <- c("darkblue","orange","red","brown","pink","dodgerblue")  
risk.bins = c(0, 6.59, 6.99, 7.51, 7.99, 8.51, 14)
risk.pal = colorBin(col_types, bins = risk.bins, na.color = "#aaff56")
rad <-3*seq(1,4,length.out = 16)
CRB_pH$sizes <- rad[as.numeric(cut(CRB_pH$count, breaks=16))]



```

Finally, plot it spatially via leaflet
```{r}
library(mapview)

phMap = leaflet(data=CRB_pH) %>% 
      #addTiles() %>% for simple openstreet basemap
      addProviderTiles(providers$Esri.NatGeoWorldMap) %>%  
      addCircleMarkers(~dec_lon_va, ~dec_lat_va,
                       fillColor = ~risk.pal(max),
                       radius = 2,  # to make size a function of count replace with ~sizes
                       fillOpacity = 0.8, opacity = 0.8,stroke=FALSE,
                       popup=~station_nm) %>%
      addLegend(position = 'bottomleft',
                pal=risk.pal,
                values=~max,
                opacity = 0.8,
                labFormat = labelFormat(digits = 1), 
                title = 'Max pH Value') %>% 
  addMouseCoordinates(style = "basic") %>% 
  setView(lng = -118.3,
          lat = 45.6,
          zoom = 5.45)

phMap

```





  
Explore the calcium data
```{r}
CRB_Ca = CRB_qw %>% 
    filter(CharacteristicName == "Calcium")

ggplot(CRB_Ca, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()

```

Appears to have a little of different units, so let's clean it up.
1. Limit data to just 'dissolved' and 'total'.
2. Covert ug/l to mg/l
```{r}
CRB_Ca = CRB_qw %>% 
  filter(CharacteristicName == "Calcium") %>% 
  
  #get rid of white spaces
  mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")) %>%   
  #limit to just dissolved and total Ca
  filter(ResultSampleFractionText %in% c("Dissolved", "Total")) %>%   
  
  # convert ug/l to mg/l
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "ug/l" ~ (ResultMeasureValue/1000),TRUE~ as.numeric(ResultMeasureValue))) %>% 
    
  # recode ug/l to mg/l
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "ug/l", "mg/l",
                    ResultMeasure.MeasureUnitCode))
  

ggplot(CRB_Ca, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```

Better, but still a lot of units that are not mg/l

```{r}
unique(CRB_Ca$ResultMeasure.MeasureUnitCode)
```

Let's only keep value that have mg/l units and add a month column. We may want to consider calcium carbonate (CaCO3) for future analyses though. 

```{r}
CRB_Ca = CRB_qw %>% 
  filter(CharacteristicName == "Calcium") %>% 
  
  #get rid of white spaces
  mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")) %>%   
  #limit to just dissolved and total Ca
  filter(ResultSampleFractionText %in% c("Dissolved", "Total")) %>%   
  
  # convert ug/l to mg/l
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "ug/l" ~ (ResultMeasureValue/1000),TRUE~ as.numeric(ResultMeasureValue))) %>% 
    
  # recode ug/l to mg/l
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "ug/l", "mg/l",
                    ResultMeasure.MeasureUnitCode)) %>% 
  
  #limit to just mg/l
  filter(ResultMeasure.MeasureUnitCode =="mg/l") %>% 
  
  #add a Month column in case we want to evaluate sampling timing
    mutate(Month = month(ActivityStartDate, label=TRUE))
  
ggplot(CRB_Ca, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```


Should we get ride of outliers? Here, I removed any value > 97.5th percentile
```{r}
CRB_Ca_out = CRB_Ca %>%
  filter(!ResultMeasureValue > quantile(ResultMeasureValue, 0.975)) 

ggplot(CRB_Ca_out, aes(x = ResultMeasure.MeasureUnitCode, y = ResultMeasureValue))+
  geom_boxplot()
```

  
When are Ca samples collected? Most are in summer... do we want to restrict Ca to non-winter (i.e., mussel growing season)?
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(CRB_Ca_out, aes(x = Month))+
  geom_histogram(stat="count")
```

   
How many samples have been collected at each site? Let's group the data by site and calculate some summaries 
```{r, eval=FALSE}
CRB_Ca_summ = CRB_Ca_out%>% 
group_by(MonitoringLocationIdentifier) %>%
      summarise(count=n(),
                start=min(ActivityStartDate),
                end=max(ActivityStartDate),
                max = max(ResultMeasureValue, na.rm = TRUE),
                mean = mean(ResultMeasureValue, na.rm = TRUE),
                stdev = sd(ResultMeasureValue, na.rm = TRUE))
```
 
    
Dot plot to view the # of data points at a site relative to pH stdeviation. Do we want to get rid of sites with a stdev > 1? 
```{r warning=FALSE}
ggplot(CRB_Ca_summ, aes(x = count, y = stdev))+
  geom_point()+
  scale_y_continuous(limits = c(0,60))
```   
   

Look at data spatially using leaflet.
Put all the critical code together, then join site info.
```{r warning=FALSE}
CRB_Ca = CRB_qw %>% 
  filter(CharacteristicName == "Calcium") %>% 
  mutate(ResultMeasure.MeasureUnitCode = 
             str_trim(ResultMeasure.MeasureUnitCode, side = "both")) %>%   
  filter(ResultSampleFractionText %in% c("Dissolved", "Total")) %>%   
  mutate(ResultMeasureValue = case_when(ResultMeasure.MeasureUnitCode == "ug/l" 
         ~ (ResultMeasureValue/1000),TRUE~ as.numeric(ResultMeasureValue))) %>% 
  mutate(ResultMeasure.MeasureUnitCode, ResultMeasure.MeasureUnitCode =
             ifelse(ResultMeasure.MeasureUnitCode == "ug/l", "mg/l",
                    ResultMeasure.MeasureUnitCode)) %>% 
  filter(ResultMeasure.MeasureUnitCode =="mg/l") %>%
  filter(!ResultMeasureValue > quantile(ResultMeasureValue, 0.975)) %>% 
  mutate(Month = month(ActivityStartDate, label=TRUE)) %>% 
  mutate(MonthQuality = ifelse(Month %in% c("Jun", "Jul", "Aug", "Sep"), "HighQuality", "LowQuality")) %>% 
    filter(MonthQuality == "HighQuality") %>%  #limit data to summer months
  group_by(MonitoringLocationIdentifier) %>%
      summarise(count=n(),
                start=min(ActivityStartDate),
                end=max(ActivityStartDate),
                max = max(ResultMeasureValue, na.rm = TRUE),
                mean = mean(ResultMeasureValue, na.rm = TRUE)) %>% 
    left_join(siteInfo, by = "MonitoringLocationIdentifier") # join location information
```


Next enter parameters for mapping on leaflet.
You can change Ca breakpoints in the risk.bins line.  I followed Whittier et al. 2008, with who "defined risk based on calcium concentrations as: very low (< 12 mg L???1), low (12-20 mg L???1), moderate (20-28 mg L???1), and high (> 28 mg L???1)". 
```{r}

col_types <- c("darkblue","pink", "orange","red")  
risk.bins = c(0, 11.99, 19.99, 27.99, 20000)
risk.pal = colorBin(col_types, bins = risk.bins, na.color = "#aaff56")
rad <-3*seq(1,4,length.out = 16)
CRB_Ca$sizes <- rad[as.numeric(cut(CRB_Ca$count, breaks=16))]


```

Finally, plot it spatially via leaflet
```{r}
CaMap = leaflet(data=CRB_Ca) %>% 
      #addTiles() %>% for simple openstreet basemap
      addProviderTiles(providers$Esri.NatGeoWorldMap) %>%  #This is cool... https://rstudio.github.io/leaflet/basemaps.html
      addCircleMarkers(~dec_lon_va,~dec_lat_va,
                       fillColor = ~risk.pal(max),
                       radius = 2,  # to make size a function of count replace with ~sizes
                       fillOpacity = 0.8, opacity = 0.8,stroke=FALSE,
                       popup=~station_nm) %>%
      addLegend(position = 'bottomleft',
                pal=risk.pal,
                values=~max,
                opacity = 0.8,
                labFormat = labelFormat(digits = 1), 
                title = 'Max Ca Value') %>% 
  mapview::addMouseCoordinates(style = "basic") %>% 
  setView(lng = -118.3,
          lat = 45.6,
          zoom = 5.45)

CaMap
```


My attempt to look at both the pH and Ca maps
```{r}
latticeview(CaMap, phMap)
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

